Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2019-07-04 unimodular-covers.tex
made proof of Lemma a new section. Put old stuff in the appendix

@@

Our proof of \Cref{thm:cayley} is based on the following result:

@@

We now turn our attention to \emph{prismatoids}, defined in~\cite{Santos-hirsch} as polytopes whose vertices all lie in two parallel facets. Since we are only interested in lattice polytopes, we here use \emph{prismatoid} meaning any $d$-polytope of the form
\[
\conv(Q_1\times\{0\} \cup Q_2 \times \{k\},
\]
with $k\in \Z_{>0}$ and $Q_1,Q_2$ being lattice $(d-1)$-polytopes. This generalizes Cayley sums, which are the case $k=1$.

@@

both smooth prismatoids and dilations of lattice polytopse of width 1

is a particular case of the following situation.

\appendix
\section{Attempt at the proof of \Cref{lemma:cayley}}

@@

>>>>

\tableofcontents

@@

Our proof of \Cref{thm:cayley} is based on the following result, the proof of which we postpone to \Cref{sec:the_lemma}:

@@

We now turn our attention to \emph{prismatoids}, defined in~\cite{Santos-hirsch} as polytopes whose vertices all lie in two parallel facets. Since we are only interested in lattice polytopes, we here use \emph{prismatoid} meaning any $d$-polytope of the form
\[
\conv(Q_1\times\{0\} \cup Q_2 \times \{k\}),
\]
with $k\in \Z_{>0}$ and $Q_1,Q_2$ being lattice $(d-1)$-polytopes. This generalizes Cayley sums, which are the case $k=1$.

@@

\section{Proof of \Cref{lemma:cayley}}
\label{sec:the_lemma}

@@

\appendix

\section{Old stuff}
